%-------------------------
% Resume in LaTeX (Jake Gutierrez template)
% Rafael Ode Brino (edited)
%-------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins (template style)
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ATS / machine readable
\pdfgentounicode=1

%-------------------------
% Custom commands (template)
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rafael Ode Brino} \\ \vspace{2pt}
    \small Brest, France $|$ Dual nationality: German \& Brazilian \\ \vspace{2pt}
    \small +33 7 45 75 03 71 $|$
    \mbox{\href{mailto:rafael.ode\_brino@ensta.fr}{\underline{\nolinkurl{rafael.ode_brino@ensta.fr}}}}$|$
    \href{https://linkedin.com/in/odebrino}{\underline{linkedin.com/in/odebrino}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {ENSTA --- National School of Advanced Techniques}{Brest, France}
    {Engineering Degree --- Observation Systems \& AI (expected 2027)}{2025 -- Present}
    \resumeItemListStart
      \resumeItem{Coursework: Artificial Intelligence \& Decision Support.}
    \resumeItemListEnd

  \resumeSubheading
    {Federal University of Rio Grande do Sul (UFRGS)}{Porto Alegre, RS, Brazil}
    {Double degree --- BSc in Electrical Engineering (expected 2028)}{2023 -- Present}
    \resumeItemListStart
      \resumeItem{Coursework: Signals and Systems.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
  {\textbf{Augmented Reality Simulation for Medical Training (ENSTA)} $|$ \emph{C\#, C++, Python}}{2025 -- Present}
  \resumeItemListStart
    \resumeItem{Designed a real-time perception pipeline for tracking and image analysis; trained and validated ML components in Python (PyTorch).}
    \resumeItem{Developed native C++ modules for real-time 6D pose estimation/tracking prototypes and integrated them into Unity as a native plugin via C\# interop (bindings), iterating through testing to improve runtime stability and robustness.}
  \resumeItemListEnd


  \resumeProjectHeading
    {\textbf{Waveforms \& Modulations (ENSTA)} $|$ \emph{MATLAB, Signal Processing}}{Jan.\ 2026}
    \resumeItemListStart
      \resumeItem{Simulated an end-to-end digital transmission chain (OOK \& DSSS) over an AWGN channel and measured BER across operating conditions.}
      \resumeItem{Built reusable modules for modulation/demodulation, spectral analysis (FFT/fftshift), and BER evaluation.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Mass Estimation via Computer Vision (UFRGS)} $|$ \emph{Python, PyTorch, OpenCV}}{2024 -- 2025}
    \resumeItemListStart
      \resumeItem{Built a supervised regression model to estimate object mass from images; created the dataset and applied advanced preprocessing.}
      \resumeItem{Performed evaluation and error analysis to improve stability and reproducibility.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Forest Mapping with Detection and SLAM (UFRGS)} $|$ \emph{Python, OpenCV}}{2024 -- 2025}
    \resumeItemListStart
      \resumeItem{Implemented a 3D mapping pipeline combining stereo visual odometry, 3D triangulation, and EKF-SLAM.}
      \resumeItem{Validated tracking stability and trajectory accuracy across multiple scenarios under near-embedded constraints.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Project Contributor}{2024 -- 2025}
    {AgroView (Startup)}{Porto Alegre, RS, Brazil}
    \resumeItemListStart
      \resumeItem{Built a computer vision prototype for early detection of stress and deterioration in lettuce plants (Python, OpenCV).}
      \resumeItem{Improved prediction reliability through experimental validation in real conditions and iterative pipeline refinement.}
    \resumeItemListEnd

  \resumeSubheading
    {Volunteer}{2019 -- 2025}
    {High School (CEAT)}{Lajeado, RS, Brazil}
    \resumeItemListStart
      \resumeItem{President (2022): Led the organization of the school’s annual Gincana—a student-run competition that builds leadership and organizational skills through theoretical and hands-on challenges—and, as a result, it enables yearly food and hygiene donation drives that exceed half a ton, as well as large-scale blood donation campaigns.}

    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming}{: Python, MATLAB, C, C++, C\#, Java} \\
    \textbf{Computer Vision \& ML}{: YOLO (detection/segmentation/training), OpenCV (image processing, tracking), Vision Transformers, supervised regression} \\
    \textbf{Signal Processing}{: OOK, DSSS, AWGN, FFT/fftshift spectral analysis, BER evaluation} \\
    \textbf{SLAM \& Estimation}{: stereo visual odometry, 3D triangulation, EKF-SLAM, sensor fusion} \\
    \textbf{Tools}{: Unity, Git/GitHub, Linux, Bash, LaTeX, Jupyter, VS Code, PyCharm, CLion, Rider}
  }}
\end{itemize}

%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    English: Bilingual - Fluent \ $|$ French: Advanced \ $|$ German: Elementary \ $|$ Portuguese: Native
  }}
\end{itemize}





\end{document}
